\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2020-12-23 manuscript.Rnw
Updates to model taxonomy section

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1), [t_1, t_2), \ldots, [t_C, t_{C+1})\}$ with each interval $0,\ldots, C$ known as a model cycle. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

@@

In $N$-state model, $N-1$ non-mutually exclusive survival curves are required. The cumulative survival function, $S_n(t)$, represents the probability that a patient survives to health state $n$ or to a lower indexed state beyond time $t$. The probability that a patient is in health state 1 is $S_1(t)$. State membership in health states $2,\ldots, N-1$ is computed as $S_{n}(t) - S_{n-1}(t)$. Finally, the probability of being in the final health state $n$ (i.e., the death state) is $1-S_{N-1}(t)$, or one minus overall survival function.

Survival functions are estimated by fitting parametric or flexible parametric survival models as described in Section~\ref{sec:iCTSTMs}. The $n$th fitted survival model with density $f_n(t)$ has cumulative density function $F_n(t)$, survivor function $1 - F_n(T)$, cumulative hazard $H_n(t) = -\log S_n(t)$, and hazard $h_n(t) = f_n(t)/S_n(t)$. State probabilities for each health states can be computed for an arbitrarily fine grid of time points to produce the health state vector $x_t$ for each time $t$ in the grid. Costs and QALYs are then computed in the same manner as in the cohort model described in Section~\ref{sec:cDTSTMs}.

>>>>

\subsection{Cohort discrete time state transition models} \label{sec:cDTSTMs}
cDTSTMs simulate the probability that a cohort of patients is in each of $H$ health states over time. Time is partitioned into intervals $\{[0, t_1), [t_1, t_2), \ldots, [t_C, t_{C+1})\}$ with each interval $0,\ldots, C$ reffered to as a model cycle. We denote $t_c$ as the time at the start of model cycle $c$. An $H \times 1$ state vector that stores the probability of being in each health state at cycle $c$ is written as $x_c = (x_{1c}, x_{2c}, \ldots, x_{Hc})$ where $\sum_h x_{hc} = 1$. A transition probability matrix is an $H \times H$ matrix denoted by $P_c$ where the $(r,s)$th element represents a transition from state $r$ to state $s$ between model cycles $c$ and $c+1$. The state vector at cycle $c+1$ for each of $C$ model cycles is given by,

@@

In an $N$-state model, $N-1$ non-mutually exclusive survival curves are required. The cumulative survival function, $S_n(t)$, represents the probability that a patient survives to health state $n$ or to a lower indexed state beyond time $t$. The probability that a patient is in health state 1 is $S_1(t)$. State membership in health states $2,\ldots, N-1$ is computed as $S_{n}(t) - S_{n-1}(t)$. Finally, the probability of being in the final health state $n$ (i.e., the death state) is $1-S_{N-1}(t)$, or one minus overall survival function.

Survival functions are estimated by fitting parametric or flexible parametric survival models as described in Section~\ref{sec:iCTSTMs}. The $n$th fitted survival model with density $f_n(t)$ has cumulative density function $F_n(t)$, survivor function $1 - F_n(T)$, cumulative hazard $H_n(t) = -\log S_n(t)$, and hazard $h_n(t) = f_n(t)/S_n(t)$. State probabilities for each health state, $x_{hc}$, can be computed for an arbitrarily fine grid of time periods $c$. Costs and QALYs are then computed in the same manner as in the cohort model described in Section~\ref{sec:cDTSTMs}.
